---
title: Integrated Learning Environment
subtitle: Using Slidify
author: Ramnath Vaidyanathan
job: Assistant Professor, McGill 
license: by-nc-sa
hitheme: solarized_dark
framework: opencpu
--- 

<style>
body {
  background-color: white;
}
</style>

--- &opencpusmall sno:0 .span8 .offset1

```{r echo = F, cache = F}
knit_hooks$set(source = function(x, options){
  if (!is.null(options$knitCode) && (options$knitCode)){
    paste("<div><textarea class='knitCode' style='display:none;'>", x, 
      "</textarea></div>", sep = '\n')
  } else {
    stringr::str_c("\n\n```", tolower(options$engine), "\n", x, "```\n\n")
  }
})
```


#### Execute Code

Inheritance is a tricky concept, so let's go through it step by step.

Inheritance is the process by which one class takes on the attributes and methods of another, and it's used to express an is-a relationship. For example, a cartoon fox is a cartoon mammal, so a CartoonFox class could inherit from a CartoonMammal class. However, a Wizard is not an Elf , so it shouldn't inherit from the Elf class (even if they have a lot of magical attributes and methods in common). Instead, both Wizard and Elf could ultimately inherit from the same MagicalBeing class.

```{r eval = F, knitCode = TRUE}
require(ggplot2)
qplot(x = wt, y = mpg, data = mtcars)

## your turn

```


*** =task

Check out the code in the editor. We've defined a class, ApplicationError, as well as a SuperBadError class that inherits from ApplicationError. Note that we don't define the display_error method in the body of SuperBadError, but it will still have access to that method via inheritance. Click Run to see for yourself!
